%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\resumeIt}[1]{
  \item\small{ #1 }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadin}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\definecolor{maroon}{rgb}{0.76, 0.13, 0.28}

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large \color{ao(english)} Tyler Wied} & {} \\
	Seattle, WA & \href{mailto:tjwied@gmail.com}{\color{Blue} tjwied@gmail.com} \\
	(920) 634-9618 & LinkedIn: \href{https://www.linkedin.com/in/tylerwied/}{\color{Blue} tylerwied} \\
	{} & GitHub: \href{https://github.com/tjwied/}{\color{Blue} tjwied} \\
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Data Science Skills}
  \resumeSubHeadingListStart
    \item{\small\textbf{Programming}{: Python, SQL, R, Unix/Bash, MPI, HTML}}
    \item{\small\textbf{Machine Learning}{: supervised (logistic \& linear regression, random forests, SVM), unsupervised (PCA, k-means clustering), natural language processing, network analysis, simulations}}
    \item{\small\textbf{Statistics}{: bootstrap, ANOVA, $\chi^2$ tests, A/B tests}}
    \item{\small\textbf{Tools}{: pandas, scikit-learn, NumPy, Jupyter, Matplotlib, Seaborn, Git, gensim, NLTK, Dash}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Insight Data Science}{Seattle, WA}
      {Data Science Fellow}{Jan 2019 - Present}
      \resumeItemListStart
	\resumeIt{Consulted for a hedge fund to identify key trends across five major cryptocurrencies.}
	\resumeIt{Developed project roadmap and architected solution using  \textbf{\color{maroon} machine learning} (NLP, topic modeling, sentiment analysis, network analysis).}
	\resumeIt{Delivered results in an interactive dashboard that displays networks, attitude levels, and the top 20 topics across \textbf{\color{maroon} 200k+ Tweets and 25k+ Twitter users}.}
      \resumeItemListEnd

    \resumeSubheading
      {Johns Hopkins University School of Medicine}{Baltimore, MD}
      {Post-Doctoral Research Fellow \& PhD Candidate}{2012 - 2019}
      \resumeItemListStart
	\resumeIt{Discovered important flexibility in a protein essential for cognitive function from \textbf{\color{maroon} 10+ TB of simulation data}, numerical analysis, and \textbf{\color{maroon} unsupervised machine learning} (PCA).}
	\resumeIt{Developed algorithm to \textbf{\color{maroon} automatically classify} millions of simulation "snapshots" into a small number of discrete states to create simple, interpretable models.}
	\resumeIt{Wrote Python scripts to validate simulation results with respect to real-world observations using statistical tests ($\chi^2$ test), resulting in \textbf{\color{maroon} 6-fold improvement} over previous predictions.}
	\resumeIt{Achieved 10x simulation speed-up by \textbf{\color{maroon} parallelizing} jobs on cluster compute nodes (MPI).}
	\resumeIt{Collaborated cross-functionally to identify promising targets in a toxin study by combining diverse datasets and identifying key features, \textbf{\color{maroon} reducing search space more than 90\%.}}
	\resumeIt{Trained and led a team of undergraduate and graduate students across four research projects.}
    \resumeItemListEnd

    \resumeSubheading
    	{University of Wisconsin-Madison}{Madison, WI}
	{Research Assistant}{2009 - 2012}
	\resumeItemListStart
		\resumeIt{Developed first genetic mouse model of mania, which is now used to understand mania in humans.}
		\resumeIt{Identified \textbf{\color{maroon} 15+ statistically significant} indicators of mania (one-way ANOVA).} 
		\resumeIt{Isolated the individual contributions of key features affecting DNA stability across more than 50 experimental conditions in MATLAB, enabling prediction with those features in future studies.}

	\resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Johns Hopkins University School of Medicine}{Baltimore, MD}
      {PhD, Biophysics (National Science Foundation Graduate Research Fellow)}{2012 -- 2018}
    \resumeSubheading
      {University of Wisconsin-Madison}{Madison, WI}
      {BS, Biochemistry (Honors in Research)}{2008 -- 2012}
  \resumeSubHeadingListEnd

\end{document}
